A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-11-01 ms.tex
new figures

\todo{we ignore the $q$!}
With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
We then use \texttt{emcee} \citep{Goodman:XX, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
\begin{equation}
    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
        p(\bs{\alpha}) \, p(f) \,
        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
\end{equation}
Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.

@@

\todo{OK, so now finally we generate samples in alpha, f using emcee, and now we have inferred the cluster parameters - boo ya}

>>>>

\todo{we ignore the $q$!}
With the marginal likelihood (\equationname~\ref{eq:marglike}), we then need to specify prior probability distributions for the hyperparameters $(\bs{\alpha}, f)$, and we can then generate posterior samples for the hyperparameters;
We use uniform priors for all of these, as summarized in \tablename~\ref{tbl:hyperpriors}.
We then use \texttt{emcee} \citep{Goodman:XX, Foreman-Mackey:2013} to sample from the posterior probability distribution for the hyperparameters given all of the photometric data,
\begin{equation}
    p(\bs{\alpha}, f \given \{\bs{m}_k\}) \propto
        p(\bs{\alpha}) \, p(f) \,
        \prod_k^K p(\bs{m}_k \given \bs{\alpha}, f) \quad .
\end{equation}
Here we use 64 walkers and run for an initial 128 steps to burn-in the sampler before running for a final 1024 steps.
\figurename~\ref{fig:hierarch-corner} shows a corner plot showing all 1D and 2D marginal posterior probability distributions estimated from the samples.

@@

We also use the posterior samples from the hierarchical inference to compute the posterior probabilities that each source is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted (blue, solid lines) are \acronym{MIST} isochrones computed from 128 randomly chosen posterior samples, shifted to the distance of the given sample and extincted given the $A_V$ value of the sample.
Also plotted is the equal-mass binary sequence (green, dashed line) computed from the median posterior sample, highlighting that the cluster may contain an abundance of binary star systems.

% Notebook: Figure-hierarch-results
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/hierarch-corner.pdf}
\caption{TODO}
\label{fig:hierarch-corner}
\end{figure}

% Notebook: Figure-hierarch-results
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{figures/hierarch-results.pdf}
\caption{TODO}
\label{fig:hierarch-iso}
\end{figure}
